---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AvatarTLA

- AvatarTLA provides color palettes inspired by characters and nations from the animated series Avatar: The Last Airbender for R graphics. The package structure and syntax are modeled after the popular [wesanderson](https://github.com/karthik/wesanderson/tree/master) package.

# Installation

- You can install the development version of AvatarTLA from GitHub with:

```{r, warning = FALSE, message = FALSE}
# install.packages("devtools")
devtools::install_github("Gerardo-Manzanarez-Villasana/AvatarTLA")
```

# Usage

```{r}
library("AvatarTLA")

library(ggplot2)

# List all available palette names
names(avatar_palettes)
```

# Palette Previews

- You can inspect all available palettes using avatar_palette()

# Characters

# Aang

# Inspiration


# Color palette inspired by Aang

```{r}
avatar_palette("Aang")
```

# Toph

# Inspiration


# Color palette inspired by Toph

```{r}
avatar_palette("Toph")
```

# Mai

```{r}
avatar_palette("Mai")
```

# Suki

```{r}
avatar_palette("Suki")
```

```{r}
# Discrete bar plot with Suki palette (4 colors)
ggplot(mpg, aes(x = drv, fill = drv)) +
  geom_bar() +
  scale_fill_manual(values = avatar_palette("Suki")) +
  theme_minimal() +
  labs(
    title = "Drive Trains with Suki Palette",
    x = "Drive Train",
    y = "Count"
  ) +
  theme(legend.position = "none")
```

# Momo

```{r}
avatar_palette("Momo")
```

# Iroh

```{r}
avatar_palette("Iroh")
```

# Appa

```{r}
avatar_palette("Appa")
```

# Sokka

```{r}
avatar_palette("Sokka")
```

# Azula

```{r}
avatar_palette("Azula")
```

```{r}
# Boxplot with Azula palette (subset to 3 colors)
ggplot(iris, aes(x = Species, y = Sepal.Length, fill = Species)) +
  geom_boxplot() +
  scale_fill_manual(values = avatar_palette("Azula", 3)) +
  theme_light() +
  labs(
    title = "Sepal Length Across Species",
    x = "Species",
    y = "Sepal Length (cm)"
  )
```

# Zuko

```{r}
avatar_palette("Zuko")
```

# Katara

```{r}
avatar_palette("Katara")
```

# Ty Lee

```{r}
avatar_palette("Ty")
```

# Avatar Nations 

# Fire Nation

```{r}
avatar_palette("FireNation")
```

# Air Nomads

```{r}
avatar_palette("AirNomads")
```

# Earth Kingdom

```{r}
avatar_palette("EarthKingdom")
```

```{r}
# Continuous scatter plot with EarthKingdom palette
ggplot(diamonds[1:100, ], aes(x = carat, y = price, color = depth)) +
  geom_point(alpha = 0.8, size = 2) +
  scale_color_gradientn(colors = avatar_palette("EarthKingdom", 100, type = "continuous")) +
  theme_minimal() +
  labs(
    title = "Diamond Price vs. Carat",
    x = "Carat",
    y = "Price ($)",
    color = "Depth"
  )
```

# Water Tribe

```{r}
avatar_palette("WaterTribe")
```

# Credits

# Logo

- The logo was created by the artist [Adri Alicee Art](https://www.instagram.com/daydrawing97/?hl=es-la)

# Nation Palettes

- The nation palettes were inspired by the [tvthemes 1.3.1](https://github.com/Ryo-N7/tvthemes) package. Credit goes to its authors

# Character Palettes

- The color palettes for the characters—Suki, Mai, and Momo—were created by me with the help of the [Coolors](https://coolors.co) website
- The rest of the characters’ palettes were taken from the [Schemecolor](https://www.schemecolor.com/palettes/avatar-the-last-airbender) website. All credit goes to their respective creators

# Character Images

- The sample images shown are for illustrative purposes only. The creators of the Nickelodeon series are Michael Dante DiMartino and Bryan Konietzko

Feel free to leave character suggestions or any comments
Best regards
- Gerardo Manzanarez-Villasana
**Glochids are forever**
